\section{System Architecture}
\label{sec:system-architecture}

The system is a batch-updated data product. It does not compute expensive analytics during each user request. Instead, ingestion and scoring happen in scheduled jobs, and the API serves precomputed results to the dashboard.

\begin{figure}[H]
    \centering
    \fbox{
    \begin{minipage}{0.92\textwidth}
    \centering
    \begin{tabular}{c}
    \textbf{FinMind / Public Taiwan Stock Data} \\
    $\downarrow$ \\
    \textbf{Python Ingestion Scripts} \\
    fetch price, valuation, revenue, and financial statement data \\
    $\downarrow$ \\
    \textbf{SQLite Storage Layer} \\
    raw and cleaned tables keyed by \texttt{stock\_id} and date \\
    $\downarrow$ \\
    \textbf{Risk Scoring Pipeline} \\
    volatility, drawdown, volume, valuation, and fundamental scores \\
    $\downarrow$ \\
    \textbf{FastAPI Backend} \\
    latest ranking, stock detail, fundamentals, portfolio analysis \\
    $\downarrow$ \\
    \textbf{React/Vite Dashboard} \\
    overview, stock detail, risk factors, portfolio watchlist
    \end{tabular}
    \end{minipage}
    }
    \caption{End-to-end data monetization system architecture.}
    \label{fig:architecture}
\end{figure}

The architecture has four main layers:

\begin{enumerate}
    \item \textbf{Ingestion}: Python scripts call FinMind datasets and upsert rows into SQLite. If live data is unavailable, the demo seed generator creates deterministic sample data for reproducibility.
    \item \textbf{Storage}: SQLite stores the tracked stock universe, market data, valuation metrics, monthly revenue, financial statement metrics, risk scores, and update logs.
    \item \textbf{Processing}: the risk pipeline computes component scores and a total score for each tracked stock after data updates.
    \item \textbf{Delivery}: FastAPI exposes JSON endpoints. React/Vite renders the user-facing dashboard.
\end{enumerate}

This design keeps the prototype simple while preserving the shape of a real data product: a scheduled batch pipeline, persistent storage, precomputed analytical features, and a low-latency serving layer.
